Investigating Biases Associated with Dietary Starch Incorporation and Retention with an Oral Biofilm Model

### 2022-06-03 analysis/paper/paper.Rmd
move all filepaths from scripts to index.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  #fig.path = "frontiers/figures/",
  fig.path = "../figures/",
  fig.align = "center",
  #fig.ext = "jpg",
  fig.pos = "H",
  dpi = 300) 
library(tidyverse)
library(broom)
library(here)
library(patchwork)
# load R scripts
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/amylase-assay.R"))
## Compile refs.bib using rbbt package ##
cite_keys <- rbbt::bbt_detect_citations(list.files(pattern = ".Rmd"))
#cite_keys <- unlist(cite_keys, use.names = FALSE)
try(
  rbbt::bbt_write_bib(here("analysis/paper/refs.bib"), keys = cite_keys, overwrite = T, translator = "bibtex")
  #rbbt::bbt_update_bib(here("analysis/paper/paper.Rmd"), here("analysis/paper/refs.bib"))
)
# ## end refs.bib ##
# 
# ## Word count ##
# wd_count <- wordcountaddin::word_count()
cor_r <- signif(count_cor$estimate, 3)
cor_ci <- signif(count_cor$conf.int, 3)
cor2_r <- signif(count_cor$estimate, 3)
cor2_ci <- signif(count_cor$conf.int, 3)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  #fig.path = "frontiers/figures/",
  fig.path = "../figures/",
  fig.align = "center",
  #fig.ext = "jpg",
  fig.pos = "H",
  dpi = 300) 
library(dplyr)
library(ggplot2)
library(broom)
library(here)
library(patchwork)
plt1_ph1 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate1_photometric1.csv"),
  col_names = F)
plt1_ph2 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate1_photometric2.csv"),
  col_names = F)

plt2_ph1 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate2_photometric1.csv"),
  col_names = F)
plt2_ph2 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate2_photometric2.csv"),
  col_names = F)
# starch counts in samples
raw_counts <- readr::read_csv(here("analysis/data/raw_data/starch_counts.csv"))
# starch counts in solutions
sol_counts <- readr::read_csv(here("analysis/data/raw_data/solution_counts.csv"))
# load R scripts
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/amylase-assay.R"))
readr::write_csv(sol_corr, here("analysis/data/derived_data/sol_corr.csv"))
readr::write_csv(corr_counts, here("analysis/data/derived_data/corr_counts.csv"))
readr::write_csv(corr_comb, here("analysis/data/derived_data/corr_comb.csv"))
## Compile refs.bib using rbbt package ##
cite_keys <- rbbt::bbt_detect_citations(list.files(pattern = ".Rmd"))
#cite_keys <- unlist(cite_keys, use.names = FALSE)
try(
  rbbt::bbt_write_bib(here("analysis/paper/refs.bib"), keys = cite_keys, overwrite = T, translator = "bibtex")
  #rbbt::bbt_update_bib(here("analysis/paper/paper.Rmd"), here("analysis/paper/refs.bib"))
)
# ## end refs.bib ##
# 
# ## Word count ##
# wd_count <- wordcountaddin::word_count()
cor_r <- signif(count_cor$estimate, 3)
cor_ci <- signif(count_cor$conf.int, 3)
cor2_r <- signif(count_cor$estimate, 3)
cor2_ci <- signif(count_cor$conf.int, 3)
```
